Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy

### 2020-12-08 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
model 2

```{r, message=FALSE, warning=FALSE}
df %>% 
  ggplot(aes(x = mask_public_bool, y = case_rate_100k)) + 
  geom_point(aes(size=5, alpha=0.2), show.legend = FALSE) + 
  labs(
    title = 'Case Rate vs Mask Public Mandate', 
    x = 'Mask Mandate in Public', 
    y = 'Case Rate per 100,000')  +
  scale_x_continuous(breaks = seq(0,1,1), labels = seq(0,1,1))

df %>%
  ggplot(aes(x=mask_public_bool, y=case_rate_100k))+
  geom_jitter(shape=21, size=6, aes( fill = factor(mask_public_bool)), width=0.1)+
  theme(legend.position = 'none') +
  labs(
    title = 'Case Rate vs Mask Public Mandate',
    x = 'Mask Mandate in Public',
    y = 'Case Rate per 100,000',
    color = 'Case Rate'
  ) +
  scale_x_continuous(breaks = seq(0,1,1), labels = seq(0,1,1))

>>>>

```{r, message=FALSE, warning=FALSE}
df %>% 
  ggplot(aes(x = factor(mask_public_bool), y = case_rate_100k)) + 
  geom_point(aes(size=5, alpha=0.2), show.legend = FALSE) + 
  labs(
    title = 'Case Rate vs Mask Public Mandate', 
    x = 'Mask Mandate in Public', 
    y = 'Case Rate per 100,000')  +
  scale_x_discrete(labels=c("0","1"))

df %>%
  ggplot(mapping = aes(factor(mask_public_bool), case_rate_100k))+
  geom_jitter(shape=21, size=6, aes( fill = factor(mask_public_bool), alpha=0.5), width=0.1)+
  theme(legend.position = "none") +
  labs(
    title = 'Case Rate vs Mask Public Mandate', 
    x = 'Mask Mandate in Public', 
    y = 'Case Rate'
  ) +
  scale_x_discrete(labels=c("No","Yes"))
